First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-06-23 eg6-letters/coherent/dvcs_he4_prl.tex
remove line numbers
typo corrections
dvcs_he4_prl.tex:  litterature->literature

\RequirePackage{lineno}
%\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%
\def\Dirac#1{#1\hskip-5pt/}
%
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
\renewenvironment{#1}%
{\linenomath\csname old#1\endcsname}%
{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
\patchAmsMathEnvironmentForLineno{#1}%
\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
\patchBothAmsMathEnvironmentsForLineno{equation}%
\patchBothAmsMathEnvironmentsForLineno{align}%
\patchBothAmsMathEnvironmentsForLineno{flalign}%
\patchBothAmsMathEnvironmentsForLineno{alignat}%
\patchBothAmsMathEnvironmentsForLineno{gather}%
\patchBothAmsMathEnvironmentsForLineno{multline}%
}

%
\begin{document}
\linenumbers

@@

We selected events with $Q^{2}$ greater than 1~GeV$^{2}$ for which the DVCS handbag 
diagram is believed to be dominant. Then the exclusivity of the reaction was ensured by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity variables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
additional details). We also 
rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 3200 events passed all these requirements, their kinematic 
distributions\footnote{We use here and for other results 
$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$.
This makes it easier to compare these results with the proton DVCS data
available in the litterature.} are shown in Fig.~\ref{fig:kin-coverage}.

@@

%Acknowledgments
The authors thank the staff of the Accelerator and Physics Divisions at the 
Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional 
de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian 
Instituto Nazionale di Fisica Nucleare, the French Centre National de la 
Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
U.S. Department of Energy, the UK Science and Technology Facilities Council 
(STFC), the Scottish Universities Physics Alliance (SUPA), the National 
Research Foundation of Korea, and the Office of Research and Economic 
Development at Mississippi State University.  The author (M.~Hattawy) also 
acknowledge the support of the Consulat G\'en\'eral de France \`a J\'erusalem. 
The Southeastern Universities Research Association operates the Thomas 
Jefferson National Accelerator Facility for the United States Department of 
Energy under contract DE-AC05-06OR23177.

>>>>

%\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%
\def\Dirac#1{#1\hskip-5pt/}
%

\begin{document}

@@

We selected events with $Q^{2}$ greater than 1~GeV$^{2}$ for which the DVCS handbag 
diagram is believed to be dominant. Then the exclusivity of the reaction was ensured by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity variables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
additional details). We also 
rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 3200 events passed all these requirements, their kinematic 
distributions\footnote{We use here and for other results 
$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$.
This makes it easier to compare these results with the proton DVCS data
available in the literature.} are shown in Fig.~\ref{fig:kin-coverage}.

@@

%Acknowledgments
The authors thank the staff of the Accelerator and Physics Divisions at the 
Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional 
de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian 
Instituto Nazionale di Fisica Nucleare, the French Centre National de la 
Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
U.S. Department of Energy, the UK Science and Technology Facilities Council 
(STFC), the Scottish Universities Physics Alliance (SUPA), the National 
Research Foundation of Korea, and the Office of Research and Economic 
Development at Mississippi State University.  The author (M.~Hattawy) also 
acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem. The Southeastern Universities Research Association operates the Thomas 
Jefferson National Accelerator Facility for the United States Department of 
Energy under contract DE-AC05-06OR23177.
